### 2023-09-23 sections/awards.tex
Update awards.tex

\begin{cvhonors}
\cvhonor
{SLAS Postgraduate and Postdoctoral Research Award and Conference Grant} 
{Research support grant for my DPhil (PhD) project and travel support for the Society for Latin American Studies (SLAS) Annual Conference, {\pounds} 1,400}
{Bath, UK}
{2022}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{St Hilda's College Muriel Wise Fund and Travel and Book Grants} 
{Research support grant for my DPhil (PhD) project and allowances for participation in conferences and purchase of books, {\pounds} 2,255} 
{Oxford, UK}
{2022}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Becas Chile Doctoral Scholarship Abroad} 
{Tuition fees, transport and living expenses for pursuing a DPhil (PhD) at the University of Oxford (ANID/PFCHA/72200340), {\pounds} 160,000}
{Oxford, UK}
{2019}
\end{cvhonors}

@@

%% \begin{cvhonors}
%% \cvhonor
%% {CESS Summer School Scholarship}
%% {Financial support for the Experimental Summer School Methods at the Nuffield-USACH Centre for Experimental Social Sciences (CESS), {\pounds} 200}
%% {Santiago, Chile}
%% {2016}
%% \end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{ALACIP Methodological School Prize}
{Best methodological work at the Latin American Political Association (ALACIP) School}
{Lima, Peru}
{2015}
\end{cvhonors}

@@

%% \begin{cvhonors}
%% \cvhonor
%% {PUC Summer School Scholarship}
%% {Financial support for the Summer School in Mixed Methods at the Pontificia Universidad Cat\'olica de Chile (PUC), {\pounds} 170}
%% {Santiago, Chile}
%% {2014} 
%% \end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Comunicracia Prize}
{Best paper of the political communication area at the XI Argentine Congress of Political Science (double-blind peer-review)} %% {\pounds} 170
{Parana, Argentina}
{2013}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{FONDECYT Thesis Writing Grant}
{Financial support for MA fieldwork (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), {\pounds} 1,150}
{Santiago, Chile}
{2012}
\end{cvhonors}

>>>>

\begin{cvhonors}
\cvhonor
{ECPR Joint Sessions of Workshops Grant}
{Travel support for the European Consortium for Political Research (ECPR) Joint Sessions of Workshops, {\pounds} 1 350.}
{Toulouse, FRA}
{2023}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{SLAS Postgraduate and Postdoctoral Research Award and Conference Grant} 
{Research support grant for my DPhil (PhD) project and travel support for the Society for Latin American Studies (SLAS) Annual Conference, {\pounds} 1 400.}
{Bath, GBR}
{2022}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{St Hilda's College Muriel Wise Fund and Travel and Book Grants} 
{Research support grant for my DPhil (PhD) project and allowances for participation in conferences and purchase of books, {\pounds} 2 255.} 
{Oxford, GBR}
{2022}
\end{cvhonors}

\begin{cvhonors}
\cvhonor
{Becas Chile Doctoral Scholarship Abroad} 
{Tuition fees, transport and living expenses for pursuing a DPhil (PhD) at the University of Oxford (ANID/PFCHA/72200340), {\pounds} 160 000.}
{Oxford, GBR}
{2019}
\end{cvhonors}

@@

%% \begin{cvhonors}
%% \cvhonor
%% {CESS Summer School Scholarship}
%% {Financial support for the Experimental Summer School Methods at the Nuffield-USACH Centre for Experimental Social Sciences (CESS), {\pounds} 200}
%% {Santiago, CHL}
%% {2016}
%% \end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{ALACIP Methodological School Prize}
{Best methodological work at the Latin American Political Association (ALACIP) School.}
{Lima, PER}
{2015}
\end{cvhonors}

@@

%% \begin{cvhonors}
%% \cvhonor
%% {PUC Summer School Scholarship}
%% {Financial support for the Summer School in Mixed Methods at the Pontificia Universidad Cat\'olica de Chile (PUC), {\pounds} 170}
%% {Santiago, CHL}
%% {2014} 
%% \end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Comunicracia Prize}
{Best paper of the political communication area at the XI Argentine Congress of Political Science (double-blind peer-review).} %% {\pounds} 170
{Parana, ARG}
{2013}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{FONDECYT Thesis Writing Grant}
{Financial support for MA fieldwork (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), {\pounds} 1 150.}
{Santiago, CHL}
{2012}
\end{cvhonors}
